%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {EDITED} % Organization
    {June 2016 - September 2016} % Date(s)
    {Farringdon, London} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed and tested, from scratch, two caching databases for web scraped data and their translations. Allows faster translations and reduces the cost of translation API. }
        \item {Fast cache: Redis database used for fast retrieval. Stores most recently used translations.}
        \item {Long-cache: MariaDB Galera Cluster with SQLAlchemy master-slave configuration. Stores all translations  for web scraped data. }
        \item {Created a Private Python Package Index that is stored in an AWS server and accessible only by employees; contains all their proprietary python packages.}
        \item {Wrote a migration script: Modify all python packages to use the new system using RegEx; create a release bash script to release on GitHub and upload to the new system; release all packages with changes. }
        \item {Developed package to identify any erroneous data stored in the database caused by errors when web scraping and apply a delta to fix the value with an extrapolated one.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Coding Tutor} % Job title
    {MyKidsy Coding Classes} % Organization
    {March 2015 - November 2016} % Date(s)
    {Google Campus, Shoreditch, London} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Taught Scratch in the beginner class and HTML, JavaScript in the advanced class}
        \item {Lead classes with 5-10 students and their parents}
        \item {Debugged code, explaining mistakes and answered questions from students}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {GCSE Computing, Nower Hill High School} % Organization
    {September 2012 - April 2014} % Date(s)
    {Harrow, London} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {One-to-one support to struggling/disruptive students, teaching HTML5, CSS3, JavaScript and Java}
        \item {Emphasis on debugging code for the entire class (approx. 30 pupils), reinforcing material taught in class, teaching efficient programming practice, explaining mistakes and answering questions from students}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Intern} % Job title
    {Citrix Systems UK Ltd.} % Organization
    {24th June 2012 - 28th June. 2012} % Date(s)
    {Gerrards Cross, London} % Location
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {IT department: Shadowed technicians, working with server management and customer service.}
        \item {Testing department: Reviewed and edited design documentation for a newly created Android application.}
        \item {Sales department: Assisted in setting up for an international sales presentation for the new Android application.}
        \item {Engineering department: Peer programmed with another intern, a self-help website for Citrix customers to help solve common problems using JavaScript and JQuery.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
